\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-11 paper/paper.Rnw
Code cleanup

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
# Convert reshape2 to tidyr, melt to gather - done
#library(reshape2)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(ipapi)
library(maps)
library(moments)
#library(pander)
#library(splitstackshape) - changed cSplit to unnest
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE)
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) 
Turk <- read.csv("turk.csv", stringsAsFactors = FALSE)

gen_true_data <- function(n, r, dep=TRUE, smoothed = FALSE) {
  d <- data.frame(rmnorm(n, c(0, 0), matrix(c(1, r, r, 1), 2, 2))) ##True plot, 0.5 for sigma off-diagonals requires ~300 iterations for all lineups.
  if (dep) {
    d$X1 <- as.vector(arima.sim(list(ar=n/100), n, innov=d$X1))
    d$X2 <- as.vector(arima.sim(list(ar=n/100), n, innov=d$X2))
  }
  if (smoothed) {
    d$X1 <- as.vector(hpfilter(d$X1, freq=1, type="lambda", drift = FALSE)[[2]])
    d$X2 <- as.vector(hpfilter(d$X2, freq=1, type="lambda", drift = FALSE)[[2]])
    d <- as.data.frame(d)
  }
  d$X1 <- scale(d$X1)
  d$X2 <- scale(d$X2)
  d$t <- 1:n
  return(d)
}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE>>=
Turk <- mutate(Turk, plot = ifelse(test_param =="line", "Overlaid Lines", "Scatterplot"), 
               sign=ifelse(correlation > 0, 1, 0), smoothed=ifelse(smoothed=="yes", 1, 0))
#ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=plot)) + geom_smooth() + geom_point() + facet_grid(n~.) + scale_colour_discrete(name = "Plot Design") +  labs(title="Unsmoothed Plot Accuracy", y="Percent Correct", x="True Plot Correlation")
ggplot(data=Turk, aes(x=correlation, y=percent, colour=plot)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(y="True plot detection rate", x="Correlation") +
  theme(legend.position="bottom")
@
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are particularly weak at revealing negative correlation.}
    \label{results}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='results', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
Turk$correct <- Turk$percent*Turk$attempt
Turk$r <- round(Turk$correlation, 1)
#Turk.line <- subset(Turk, test_param=="line")
#Turk.scatter <- subset(Turk, test_param=="scatter")
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "plot")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(plot=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(plot=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(plot=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(plot=="Scatterplot", correct, 0)))
#Turk.line <- Turk.line[order(Turk.line$r, Turk.line$n, Turk.line$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.line <- summarise(group_by(Turk.line, smoothed, n, r, test_param), sum(attempt), sum(correct))
#Turk.scatter <- Turk.scatter[order(Turk.scatter$r, Turk.scatter$n, Turk.scatter$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.scatter <- summarise(group_by(Turk.scatter, smoothed, n, r), sum(attempt), sum(correct))
#colnames(Turk.scatter) <- c("smoothed", "n", "r", "s.attempt", "s.correct")
#colnames(Turk.line) <- c("smoothed", "n", "r", "l.attempt", "l.correct")
#prop <- cbind(Turk.line, Turk.scatter[4:5])
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(x="Correlation", y="Scatterplot power minus Overlaid Lines") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. The largest differences appear in negative correlation, where the scatter plot is more powerful.}
 \label{powerdiff}
\end{figure}

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='powerdiff', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(plot~.) + scale_colour_discrete(name = "Sample size") +  labs(y="Percent Correct", x="Correlation") + theme(legend.position="bottom")
@
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universaly benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
 \label{samplesize}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
full <- mutate(full, sign = ifelse(correlation >= 0, 1, 0), n24 = ifelse(n ==24, 1, 0), n48 = ifelse(n ==48,  1, 0), n96 = ifelse(n ==96, 1, 0), plot = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"))
time <- data.frame(plot=full$plot, time=full$log_time, correct=full$correct, rsgn=full$sign)
#ggplot(data=time, aes(x=time, fill=factor(correct))) +geom_bar(stat="bin") + facet_grid(~plot) +labs(x="Log(Time) Taken", y=element_blank()) + scale_fill_discrete(name = "Correct")
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, plot, rsgn), m=mean(time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2)
@
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
  \label{time} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf <- data.frame(plot=full$plot, conf=full$conf_level, correct=full$correct, rsgn=full$sign)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, plot, rsgn), m=mean(conf))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2)
@
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
  \label{confidence} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep2 <- y$Var1[y$Freq>9]
conf2 <- filter(full, subj_id %in% keep2)
conf2 <- select(conf2, conf_level, correlation, test_param, smoothed, n, correct, sign, plot, subj_id) #c(7, 15, 16, 17, 20, 27)]
#sub <- summarise(group_by(sub, subj_id), correct = sum(correct), conf=mean(conf_level))
#sub <- merge(sub, y, by.x="subj_id", by.y="Var1")
#sub <- mutate(sub, prop = correct/Freq)
qplot(correlation, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~plot+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
  \label{confidence2}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
count.setup <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
#pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#pin$response_0 <- separate(pin, response_0, "response_0", sep=",", extra="drop")
count.setup$choice <- separate(count.setup, response_0, c("choice", "l1", "l2"), ",", extra="drop")$choice
count.setup$choice[str_detect(count.setup$actual_location, count.setup$response_0)] <- 
  count.setup$actual_location[str_detect(count.setup$actual_location, count.setup$response_0)]
                         #as.integer(pin$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$choice))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plots", "count")
pin <- merge(counts, Turk[-17], by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plots, count, smoothed, true_pos, n, test_param, r, attempt)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r", "attempt")
pin <- mutate(pin, design=ifelse(design=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"), percent = count/attempt)
#pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@

  \caption{Pin plots of the subject selections of each lineup, by design, smoothness, true plot correlaition and sample size. On the x-axis is the correlation of the plot (there is potentially spurious correlation in the null plots), and on the y-axis is the proportion a plot was chosen. Each plot contains data from the three lineups with the requisite characteristics. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not seem to appear as it has a proportion of zero and is visually blocked by the red pins. Strongly correlated plot seem to be selected regardless of if the relationship is real or spurious.}
  \label{pins}
\end{figure}

@@

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.} %Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample.

\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.subs <- filter(full, subj_id %in% keep)
full.subs$r <- round(full.subs$correlation, 1)
full.subs$rsgn <- ifelse(full.subs$r >= 0, 1, 0)
full.subs$rabs <- abs(full.subs$r)
full.subs$plot <- ifelse(full.subs$test_param == 0, "S", "L")
full.subs <- select(full.subs, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location, pic_id, choice_reason)#[,c(1,7, 15,16,17,20:26)]
full.subs$attempts <- sapply(strsplit(as.character(full.subs$response_0), ","), length)
full.subs$weights = 1/(full.subs$attempts) #weights are actually number of attempts in the glm
full.sub <- full.subs %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
full.sub$alpha <- log(.05/0.95)
full.sub$subj_id <- as.numeric(full.sub$subj_id)
subsetted <- select(full.sub, rabs, n, alpha, rsgn, smoothed, plot, subj_id, weights, correct, log_time)
subsetted$rabs <- as.numeric(subsetted$rabs)
subsetted$subj_id <- as.numeric(subsetted$subj_id)
subsetted <- mutate(subsetted, plot = ifelse(plot=="S", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)

powercoef <- read.csv("sas/PowerEstimates.csv")
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
#kable(powercoef[7:12,], format="latex", digits=2)
@
\end{table}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='powerfit', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
\label{random}
\end{figure}

>>>>

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
# Convert reshape2 to tidyr, melt to gather - done
#library(reshape2)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(ipapi)
library(maps)
library(moments)
#library(pander)
#library(splitstackshape) - changed cSplit to unnest
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE)
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) 
prediction <- read.csv("sas/predfit.csv") #Large file, very slow
time.fit <- read.csv("sas/time.csv")
powercoef <- read.csv("sas/PowerEstimates.csv")

colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "design", "subj_id", "weights", "detected", "log_time", "RandomEf", "FixedEf", "residual")

full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep <- y$Var1[y$Freq>9]

full <- mutate(full, design = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"),
               r = round(correlation, 1),
               rsgn = ifelse(r >= 0, 1, 0),
               rabs=abs(r),
               alpha = log(0.05/0.95),
               attempts = sapply(strsplit(as.character(full$response_0), ","), length), #count number of selections in response_0 column
               weights = 1/attempts)
full <- full %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#split multiple selections in response_0 into different rows
full <- mutate(full, correct = ifelse(response_0 == actual_location, 1, 0),
                   score = ifelse(correct==1, (20-attempts)/19, 0))
full <- select(full, subj_id, correct, score, r, rsgn, rabs, smoothed, n, design, log_time, response_0, actual_location, pic_id, choice_reason, attempts, weights, alpha)

full.sub <- filter(full, subj_id %in% keep) #keeping only >9 selections in actual modelling to better estimate random effects

bylineup <- summarise(group_by(full.sub, pic_id, n, smoothed, design, r, actual_location), total=sum(score), correct=sum(correct), evals=sum(attempts*weights))
bylineup <- mutate(bylineup, percent = total/evals)
bylineup.sub <- summarise(group_by(full.sub, pic_id), total=sum(score), evals=sum(weights*attempts))

gen_true_data <- function(n, r, dep=TRUE, smoothed = FALSE) {
  d <- data.frame(rmnorm(n, c(0, 0), matrix(c(1, r, r, 1), 2, 2))) 
  if (dep) {
    d$X1 <- as.vector(arima.sim(list(ar=n/100), n, innov=d$X1))
    d$X2 <- as.vector(arima.sim(list(ar=n/100), n, innov=d$X2))
  }
  if (smoothed) {
    d$X1 <- as.vector(hpfilter(d$X1, freq=1, type="lambda", drift = FALSE)[[2]])
    d$X2 <- as.vector(hpfilter(d$X2, freq=1, type="lambda", drift = FALSE)[[2]])
    d <- as.data.frame(d)
  }
  d$X1 <- scale(d$X1)
  d$X2 <- scale(d$X2)
  d$t <- 1:n
  return(d)
}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE>>=
ggplot(data=bylineup, aes(x=r, y=percent, colour=design)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(y="True plot detection rate", x="Correlation") +
  theme(legend.position="bottom")
@
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are much weaker at revealing negative correlation.}
    \label{results}
\end{figure}

@@

\iffalse
\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "design")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(design=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(design=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(design=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(design=="Scatterplot", correct, 0)))
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(x="Correlation", y="Scatterplot power minus Overlaid Lines") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. The largest differences appear in negative correlation, where the scatter plot is more powerful.}
 \label{powerdiff}
\end{figure}
\fi

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
ggplot(data=subset(bylineup, smoothed==0), aes(x=r, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(design~.) + scale_colour_discrete(name = "Sample size") +  labs(y="Percent Correct", x="Correlation") + theme(legend.position="bottom")
@
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universally benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
 \label{samplesize}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
time <- select(full, design, log_time, correct,, sign)
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, design, rsgn), m=mean(log_time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=log_time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2)
@
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
    \label{time} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf <- select(full, design, conf_level, correct, sign)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, design, rsgn), m=mean(conf_level))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf_level)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(design~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2)
@
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
  \label{confidence} 
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf2 <- select(full, conf_level, correlation, smoothed, n, design) #c(7, 15
qplot(correlation, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~design+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
 \label{confidence2}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='setup', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
count.setup <- select(full, pic_id, response_0, actual_location, 
              design, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$response_0))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, bylineup, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, actual_location, n, design, r, evals)
pin$r <- factor(pin$r)
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==actual_location, "True plot", "Null plot"), percent = count/evals)
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@
  \caption{Pin plots of the subject selections of each lineup, by design, smoothness, true plot correlaition and sample size. On the x-axis is the correlation of the plot (there is potentially spurious correlation in the null plots), and on the y-axis is the proportion a plot was chosen. Each plot contains data from the three lineups with the requisite characteristics. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not seem to appear as it has a proportion of zero and is visually blocked by the red pins. Strongly correlated plot seem to be selected regardless of if the relationship is real or spurious.}
  \label{pins}
\end{figure}

@@

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
sasdata$rabs <- as.numeric(sasdata$rabs)
sasdata$subj_id <- as.numeric(sasdata$subj_id)
sasadata <- mutate(sasdata, design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
@
\end{table}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='powermodel', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}
